Verification of a Deterministic Random Bits Generator

### 2016-01-01 paper/paper.tex
modification to paper

Of what the tasks I mentioned, the ones that must be trusted are the translation of \stdtitle{NIST SP 800-90A} into functional specifications and the creation of API specifications from those functional programs. Everything else is machine-checked. Can the functional and API specifications be trusted? For the latter, I hope to make a convincing claim by the end of this paper that as long as the functional specifications are correct, the corresponding API specifications will be, too. As for the functional specifications, first of all, they are small, easy-to-reason-about, strongly typed functional programs. I also ran the programs on some test inputs from NIST and verified that the output matches. That said, it is still unsatisfying that at the functional specification level, I had to resort to unit tests. Thankfully, there is a parallel project by Katherine Ye ‘16 that will prove cryptographic properties of the functional specifications. The fact that this parallel project can be done in concurrent to (and mostly independent from) the verification of the C implementation shows the power and flexibility of VST.

@@

The name \lstinline{catastrophic_error} came from \stdtitle{NIST SP 800-90A} and is used to denote errors that are not user errors. User errors include providing an optional nonce that is too long and requesting prediction resistance when the DRBG state has not been initialized with prediction resistance capability. An example of catastrophic errors is the entropy source failing to provide the requested amount of entropy.

@@

\lstinline{Fixpoint} is a recursive function where at least one parameter is structurally getting smaller, allowing Coq to figure out the proof of termination automatically. In this case, it is the last parameter, the natural number \lstinline{count}, which is initialized with \lstinline{1}, meaning that this recursive function is only allowed to go one level deep.

@@

Even though I am verifying \stdtitle{mbedTLS} implementation of DRBG, the pre-existing verifications and specifications of SHA256 and HMAC are for the \stdtitle{OpenSSL} version. To make the two versions work with each other, I created a thin wrapper on the \stdtitle{mbedTLS} HMAC interface. For example, take the \lstinline{final} function. \stdtitle{mbedTLS} and \stdtitle{OpenSSL} have similar APIs for the \lstinline{final} function, and I connect them with this wrapper function:

>>>>

Of what the tasks I mentioned, the ones that must be trusted are the translation of \stdtitle{NIST SP 800-90A} into functional specifications and the creation of API specifications from those functional programs. Everything else is machine-checked. Can the functional and API specifications be trusted? For the latter, I hope to make a convincing claim by the end of this paper that as long as the functional specifications are correct, the corresponding API specifications will be, too. As for the functional specifications, first of all, they are small, easy-to-reason-about, strongly typed functional programs. I also ran the programs on some test inputs from NIST and verified that the output matches. That said, it is still unsatisfying that at the functional specification level, I had to resort to unit tests. Thankfully, there is a parallel project by Katherine Ye ‘16 that will prove cryptographic properties of the functional specifications. The fact that this parallel project can be done concurrent to (and mostly independent from) the verification of the C implementation shows the power and flexibility of VST.

@@

The name \lstinline{catastrophic_error} came from \stdtitle{NIST SP 800-90A} and is used to denote errors that are not user errors. An example of user errors is requesting prediction resistance when the DRBG state was not initialized with prediction resistance capability. An example of catastrophic errors is the entropy source failing to provide the requested amount of entropy.

@@

A \lstinline{Fixpoint} is a recursive function where at least one parameter is structurally getting smaller, allowing Coq to figure out the proof of termination automatically. In this case, it is the last parameter, the natural number \lstinline{count}, which is initialized with \lstinline{1}, meaning that this recursive function is only allowed to go one level deep.

@@

Even though I am verifying \stdtitle{mbedTLS} implementation of DRBG, the pre-existing verifications and specifications of SHA-256 and HMAC are for the \stdtitle{OpenSSL} version. To make the two versions work with each other, I created a thin wrapper on the \stdtitle{mbedTLS} HMAC interface. For example, take the \lstinline{final} function. \stdtitle{mbedTLS} and \stdtitle{OpenSSL} have similar APIs for the \lstinline{final} function, and I connect them with this wrapper function:
